\vfill A Testing Framework for Web Applications

### 2014-03-17 Paper/paper.tex
Super basic introduction expansion.

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others. \cite{EvolutionOfWeb} In that same time period, the number of global internet users has grown to somewhere around 2.5 billion people. \cite{EvolutionOfWeb} The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.
Like any piece of software, these web applications require testing in order to determine their correctness and give their users the best experience possible. Unfortunately, web applications are new and there are no standard practices regarding how to test them. Their dynamic nature and network communication require a different testing toolkit than their predecessors. In addition, web applications are being produced at an incredible rate and so there's a need for rapid testing.

We can see that this is not a solved problem by looking at some of the biggest web application around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on. \cite{ErrorsInTheWild} That may seem like a incredibly small amount for such monoliths, and, honestly, it is fairly small, but those are still errors in the software that ought to be fixed.
What this all boils down to is that there needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, quick to develop on, and thorough in its coverage.

\subsection{What Has Been Done Already?}
- Info info info

\subsubsection{Why It Is Insufficient}
- No standard
- Info info info

>>>>

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others. \cite{EvolutionOfWeb} In that same time period, the number of global internet users has grown to somewhere around 2.5 billion people. \cite{EvolutionOfWeb} The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.

Like any piece of software, these web applications require testing in order to determine their correctness and give their users the best experience possible. Unfortunately, web applications are new and there are no standard practices regarding how to test them. Their dynamic nature and network communication require a different testing toolkit than their predecessors. In addition, web applications are being produced at an incredible rate and so there's a need for rapid testing.

We can see that this is not a solved problem by looking at some of the biggest web application around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on. \cite{ErrorsInTheWild} That may seem like a incredibly small amount for such monoliths, and, honestly, it is fairly small, but those are still errors in the software that ought to be fixed.

What this all boils down to is that there needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, quick to develop on, and thorough in its coverage.

\subsection{What Has Been Done Already?}
Web developers are not clueless, they understand that there is a need for testing of web applications. Unfortunately, web development is still a relatively new domain and developers did not come together to work on the problem of testing but rather came up with their own proprietary solutions in isolation or merely on a per-project basis. Some of these tools gained traction and become larger, more general, tools. 
- Info info info

\subsubsection{Why It Is Insufficient}
- No standard
The problem that followed was that many of the tools attempted to remedy the same problems and so a developer would have to decide between a number of similar tools. Having to wade through a sea of similar tools is time-consuming and that can be the death of a cutting-edge application. The more time an application is off the market, the more time competitors have to develop their own versions. Yet another problem is that deciding between similar tools can be discouraging to the developer that just wants to write their application and test it quickly.

- Info info info
